---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(zoo)
library(GGally)
library(modelr)
```


```{r}
avocado <- read_csv("data/avocado.csv")
```

```{r}
glimpse(avocado)
summary(avocado)
```

```{r}
unique(avocado$region)
```

```{r}
avocado_trim <- avocado %>%
  #create a variable for seasons
  mutate(seasons = factor(
    format(as.yearqtr(as.yearmon(Date, "%m/%d/%Y") + 1/12), "%q"),
    levels = 1:4, 
    labels = c("winter", "spring", "summer", "fall"))) %>%
  mutate(type = as_factor(type),
         region = as_factor(region)) %>%
  #remove unwanted variables
  select(-c("X1", "Date", "Total Bags", "region")) %>%
  clean_names()
```

```{r}
alias(average_price ~ ., data = avocado_trim)
```

```{r}
avo_numeric <- avocado_trim %>%
  select_if(is.numeric)

avo_nonumeric <- avocado_trim %>%
  select_if(function(x) !is.numeric(x))

avo_nonumeric$average_price <-avocado_trim$average_price
```


```{r}
ggpairs(avo_numeric)
```
I identified x4046 as having the highest numeric correlation, so I will investigate that first
```{r}
ggpairs(avo_nonumeric)
```
I will also want to investigate type as there is a difference in distribution

```{r}
mod1a <- lm(average_price ~ x4046, data = avocado_trim)
summary(mod1a)
```

```{r}
mod1b <- lm(average_price ~ total_volume, data = avocado_trim)
summary(mod1b)
```

```{r}
mod1c <- lm(average_price ~ type, data = avocado_trim)
summary(mod1c)
```
Type seems to be the most promising 

```{r}
par(mfrow = c(2,2))
plot(mod1c)
```

```{r}
avo_resid <- avocado_trim %>%
  add_residuals(mod1c) %>%
  select(-c("average_price", "type"))

avo_resid_numeric <- avo_resid %>%
  select_if(is.numeric)

avo_resid_nonumeric <- avo_resid %>%
  select_if(function(x) !is.numeric(x))

avo_resid_nonumeric$resid <- avo_resid$resid
```

```{r}
ggpairs(avo_resid_numeric)
```

```{r}
ggpairs(avo_resid_nonumeric)
```

Year has the highest correlation. I will also have a look at x4046 and seasons

```{r}
mod2a <- lm(average_price ~ type + year, data = avocado_trim)
summary(mod2a)
  
```

```{r}
mod2b <- lm(average_price ~ type + x4046, data = avocado_trim)
summary(mod2b)
```

```{r}
mod2c <- lm(average_price ~ type + seasons, data = avocado_trim)
summary(mod2c)
```
Seasons has a higher r^2 so I'll continue using mod2c

```{r}
avo_resid <- avocado_trim %>%
  add_residuals(mod2c) %>%
  select(-c("average_price", "type", "seasons"))

```

```{r}
ggpairs(avo_resid)
```

```{r}
par(mfrow = c(2,2))
plot(mod2c)
```

```{r}
mod3a <- lm(average_price ~ type + seasons + year, data = avocado_trim)
summary(mod3a)
```

```{r}
mod3b <- lm(average_price ~ type + seasons + x4046, data = avocado_trim)
summary(mod3b)
```

```{r}
par(mfrow = c(2,2))
plot(mod3a)
```

```{r}
avo_resid <- avocado_trim %>%
  add_residuals(mod3a) %>%
  select(-c("average_price", "type", "seasons", "year"))
ggpairs(avo_resid)
```

```{r}
mod4a <- lm(average_price ~ type + seasons + year + x4046, data = avocado_trim)
summary(mod4a)
```

```{r}
mod4b <- lm(average_price ~ type + seasons + year + large_bags, data = avocado_trim)
summary(mod4b)

```

```{r}
mod4c <- lm(average_price ~ type + seasons + year + total_volume, data = avocado_trim)
summary(mod4c)
```

```{r}
par(mfrow = c(2,2))
plot(mod4a)
```

```{r}
mod5a <- lm(average_price ~ type + seasons + year + x4046 + type:seasons, data = avocado_trim)
summary(mod5a)
```

```{r}
mod5b <- lm(average_price ~ type + seasons + year + x4046 + type:year, data = avocado_trim)
summary(mod5b)
```

```{r}
mod5c <- lm(average_price ~ type + seasons + year + x4046 + type:x4046, data = avocado_trim)
summary(mod5c)
```

```{r}
mod5d <- lm(average_price ~ type + seasons + year + x4046 + seasons:year, data = avocado_trim)
summary(mod5d)
```
this model had the highest r^2 but year was insignificant 
```{r}
mod5e <- lm(average_price ~ type + seasons + year + x4046 + seasons:x4046, data = avocado_trim)
summary(mod5e)
```
```{r}
mod5f <- lm(average_price ~ type + seasons + year + x4046 + year:x4046, data = avocado_trim)
summary(mod5f)
```

```{r}
par(mfrow = c(2,2))
plot(mod5b)
```

```{r}
library(relaimpo)

```

```{r}
calc.relimp(mod4a, type = "lmg", rela = TRUE)
```
I had to use previous model as the ones with interactions weren't working.
Here you can see type has the greatest importance with almost 80% of r^2
