---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)

library(readr)
library(janitor)
library(tidyverse)
```

```{r}
phones <- read_csv("data/20190928-items.csv")
```

```{r}
phones <- clean_names(phones)
glimpse(phones)
```

```{r}
phones %>%
  group_by(brand) %>%
  summarise(sum_phones = n()) %>%
  arrange(desc(sum_phones)) %>%
  head(1)
```
Samsung has the highest number of phones in the dataset.


```{r}
samsung_stats <- phones %>%
  filter(brand == "Samsung") %>%
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
samsung_stats
```
 
With a mean of 3.47 and a standard deviation of 0.68 this tells us that atleast 68% of the population lies between 2.79 and 4.15
 
```{r}
phone_plot <- phones %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stats$mean, 
      sd = samsung_stats$sd
    ),
    col = "red"
  )
phone_plot
```

The distribution of the plot is unimodal and close to normal

```{r}
phones %>%
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(phones))
```


```{r}
phones %>%
  filter(rating >= samsung_stats$mean - (samsung_stats$sd * 2)) %>%
  filter(rating <= samsung_stats$mean + (samsung_stats$sd * 2)) %>%
  summarise(prop_within_2nd = n() / nrow(phones))
```

```{r}
phones %>%
  filter(rating >= samsung_stats$mean - (samsung_stats$sd * 3)) %>%
  filter(rating <= samsung_stats$mean + (samsung_stats$sd * 3)) %>%
  summarise(prop_within_2nd = n() / nrow(phones))
```

This tells us that there is around a 78% chance of someone will rate a Samsung phone in the range of one standard deviation of the mean, which is around 2.79 to 4.15. Theres a 93% chance they will rate it two standard deviations from the mean and 98% that they will rate it Three from the mean.